Preprocessing Real-World Data

### 2022-12-20 docs/src/paper/data_preprocessing/_real_world_data.qmd
work on data

---
title: Preprocessing Real-World Data
jupyter: julia-1.7
---

```{julia}
using Pkg; Pkg.activate("dev")
```

```{julia}
include("dev/utils.jl")
using AlgorithmicRecourseDynamics
using CounterfactualExplanations, Flux, Plots, PlotThemes, Random, LaplaceRedux, LinearAlgebra
theme(:wong)
output_path = output_dir("real_world")
www_path = www_dir("real_world")
data_path = data_dir("real_world")
```

@@

Fetching the data using Python's `sklearn`:

```{python}
from sklearn.datasets import fetch_california_housing
df, y = fetch_california_housing(return_X_y=True, as_frame=True)
df["target"] = y.values
data_path = "../../artifacts/upload/data/real_world"
import os
df.to_csv(os.path.join(data_path,"raw/cal_housing.csv"), index=False)
```

@@

```{julia}
using CSV, DataFrames, Statistics, StatsBase
df = CSV.read(joinpath(data_path, "raw/cal_housing.csv"), DataFrame)
# Features:
X = Matrix(df[:,Not(:target)])
dt = fit(ZScoreTransform, X, dims=1)
StatsBase.transform!(dt, X)
# Target:
y = df.target
y = Float64.(y .>= median(y)); # binary target
# Data:
df = DataFrame(X,:auto)
df.target = y
```

>>>>

---
title: Preprocessing Real-World Data
---

```{julia}
#| echo: false

include("docs/src/paper/setup.jl")
eval(setup)
output_path = output_dir("real_world")
www_path = www_dir("real_world")
data_path = data_dir("real_world")
```

@@

Fetching the data using Python's `sklearn` (run this in the Python REPL):

```python
from sklearn.datasets import fetch_california_housing
df, y = fetch_california_housing(return_X_y=True, as_frame=True)
df["target"] = y.values
data_path = "dev/artifacts/upload/data/real_world"
import os
if not os.path.isdir(os.path.join(data_path,"raw")):
    os.makedirs(os.path.join(data_path,"raw"))
df.to_csv(os.path.join(data_path,"raw/cal_housing.csv"), index=False)
```

@@

```{julia}
df = CSV.read(joinpath(data_path, "raw/cal_housing.csv"), DataFrame)
# Features:
X = Matrix(df[:,Not(:target)])
dt = StatsBase.fit(ZScoreTransform, X, dims=1)
StatsBase.transform!(dt, X)
# Target:
y = df.target
y = Float64.(y .>= median(y)); # binary target
# Data:
df = DataFrame(X,:auto)
df.target = y
```
